---
title: 'RMarkdown:  In Class Assignment'
author: "Sandy Datta"
date: "Data 2401"
output: 
  html_document:
    toc: TRUE
    toc_depth: 3
---


```{r setup, include=FALSE}
# Everything in this chunk is R code. 
# You are not expected to understand or edit this yet. 
# We will talk about what this does in a later class, with a little preview in part 2.
knitr::opts_chunk$set(echo = TRUE) 
```


Reminders: 

- You do not need to memorize Markdown syntax.
- You are expected to look things up using:
   - RStudio’s Markdown Help
   - Online documentation or examples
- Click Knit as you go to check that your document still renders correctly.
- Commit at the end, but consider committing as you go as well. 



# Part 1: Markdown Practice

**Do not skip reading this instruction** Create a new section at the end of this section named "Your work here". In that section, complete the tasks below:

- Make a *subsection* called Wise Words. 
- Put your favorite quote in a block quote. 
- Add a working, clickable link to a website that provides more information about that quote.
- Make another *subsection* called "I recommend", and add some information about your favorite author or musician: 
  - A _subsubheading_ with the name of the artist or author;    
  - An example of their writing or lyrics (formatted in a *block of text*);   
  - A _list_ of things they have written or performed (remember to use the formatting markup for a list!), with any of the titles/names in bold.     

# Your work here

## *Wise Words*

> Here's Messi. Away from two, three, four. Wonderful, wonderful,wonderful.

[Link](https://www.youtube.com/watch?v=-tnGhY251ys)

## *I recommend*
_Future_
```
Life is good
```
- **March Madness**
- **Wicked**
- **Plutoski**

# Part 2: Code Chunks

```{r echo = FALSE}
2 + 2
```

Complete the following steps:

- Knit the document and observe what appears in the output.
- Change the chunk option echo=TRUE to echo=FALSE.
- Knit the document again.
- Finally, write 2–3 sentences answering the following questions:
  - What changed between the two outputs?
  - Did the calculation still run when the code was hidden?
  - Why might someone want to hide code in a report?
  - Why might someone want to show code in a report?
  
```
When echo=TRUE, the resulting document showed the equation "2+2" and the answer to the equation, which is 4, however, when echo=FALSE, the document only showed the answer but not the equation. The calculation still ran whether or not the code was hidden. Someone may want to hide the code in a report if they only want to show the outcome of an equation. Someone may want to show the code if they are submitting a document to be reviewed by a peer so that the reviewer can see where there was a mistake if one occured.
```  
# Part 3: A small R-in-markdown preview

- Create a subsection within this section called About this document.
- Write 2–3 sentences describing what this document is and what it produces.
- Include one value generated by inline R code.

> To include inline code, use this weird little `r 2+2` pattern, putting the code where I have 2+2 (which is code!) 
> You can use the function `Sys.Date()`, which would be added like this `r Sys.Date()` but you can do something else if you want. (Look at the knit html to see what this does.)

## About this document

```
This document is a guide that helps to understand how to use Markdown syntax. It does so by giving instructions that would require the user to use Markdown practically.
```
`r Sys.Date()`


# Submitting Instructions

When you are finished: 

- Knit the document so that it produces an html file.
- Stage, commit, and push:
  - The updated `.rmd` file 
  - The generated `.html` file
- Submit the GitHub link to the assignment on Canvas.
 
